---
title: "Mini R Project 1"
author: "Sunni Raleigh and Natalia Iannucci"
output: html_document
---

#Loading the dataset
```{r}
d <- read.table("Example 1_3 Health.txt", header = T, sep = '\t')

attach(d)
```
 
 
#####1. Perform an initial study to determine whether a simple linear regression model is reasonable to predict the number of doctors based on the number of hospitals in the city. 

#Initial study to observe the nature of the relationship between the number of hospitals and number of doctors in a city

__Graphical Method:__ Scatter Plot
```{r}
plot(NumMDs, NumHospitals, pch = 19, cex = 1.5, col = "blue", main = "scatter plot between number of doctors in a city and the number of hospitals in a city")
```

The scatter plot shows a postive linear trend.

__Numerical Method:__ Pearson Linear Correlation Coefficient 
```{r}
r <- cor(NumMDs, NumHospitals)

r
```
r value indicates there is a      linear correlation between the number of doctors in a city and the number of hospitals in a city.

__Based on the scatter plot and the r value, fitting a linear relationship is (IS OR IS NOT??????) reasonable.__
