---
title: "Mini R Project 1"
author: "Sunni Raleigh and Natalia Iannucci"
output: html_document
---

#Loading the dataset
```{r}
d <- read.table("Example 1_3 Health.txt", header = T, sep = '\t')

attach(d)
```
 
 
#####1. Perform an initial study to determine whether a simple linear regression model is reasonable to predict the number of doctors based on the number of hospitals in the city. 

#Initial study to observe the nature of the relationship between the number of hospitals and number of doctors in a city

__Graphical Method:__ Scatter Plot
```{r}
plot(NumMDs, NumHospitals, pch = 19, cex = 1.5, col = "blue", main = "Scatter plot between number of doctors in \na a city and the number of hospitals in a city")
```

The scatter plot shows a postive linear trend.

__Numerical Method:__ Pearson Linear Correlation Coefficient 
```{r}
r <- cor(NumMDs, NumHospitals)

r
```
The r value  of 0.9084686 indicates there is a strong positive linear correlation between the number of doctors in a city and the number of hospitals in a city.

__Based on the scatter plot and the r value, fitting a linear relationship is reasonable.__ 




#####2. Fit a least square regression line to predict the number of doctors based on the number of hospitals in a city.
```{r}
regMode1 <- lm(NumMDs ~ NumHospitals)
regMode1
```

NumMDs = -385.1 + 282*NumHospitals + e

$y_i = -385.1 - 282x_i + e_i$ for $i=1,2,\cdots,83$ where y is the number of doctors in a city, x is the number of hospitals in a city, and e is the random error with the assumptions $e_i \stackrel{iid}\sim N(0, \sigma^2)$.

#####3. Are you satisfied with the fit of this simple linear model?
```{r}
# find residuals
residuals <- resid(regMode1)

# find predicted values
predValues <- predict(regMode1)
```

